Box

### 2021-07-13 MS/box.Rmd
Added a first crack at cerating a temperature standardised SMD

### Sampling variance for the difference between two slopes

>>>>

### Controlling for unitary differences and temperature across studies

ARR assumes that the units for the mean difference across studies is consistent. This will often not be the case for many meta-analyses that hope to synthesise a wide diversity of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes). Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences. As such, we can apply some of the same logic we discuss above to SMD, to correct for both temperature differences. Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance. We won't re-iterate these formulas again. Just like with ARR we can apply our temperature correction to the SMD formula as follows:

$$
SMD_{T} = \frac{\left(\bar{X}_{2} - \bar{X}_{1}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
$$
Here, we can see that the difference between $X_1$ and $X_2$ is standardised by the pooled SD, essentially correcting for unitary differences. Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature. To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:

$$
s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
$$
### Sampling variance for the difference between two slopes
